The Astropy Project

### 2017-10-20 main.tex
Update on Overleaf.

In addition, classes are provided in order to identify lower and upper limits for a dataset based on specific algorithms (such as using percentiles).

Identifying lower and upper limits, as well as re-normalizing, is described in the Intervals and Normalization section, while stretching is described in the Stretching section.

@@

%\subsection{Utils}
% Lim

@@

The \astropypkg \package{stats} package provides
statistical tools that are useful for or specific to
astronomy and are not found in other \python\
statistics packages such as \package{scipy}
\citep{scipy} or \package{statsmodels}
\citep{seabold2010statsmodels}.   The
\package{stats} package contains a range of
different functionality used by many different
disciplines in astronomy.   It is not a complete set
of statistic tools, but rather a still growing
collection of useful features.

@@

\subsubsection{Robust Statistical Estimators}

>>>>

Several classes are provided for determining intervals and for normalizing values in this interval to the [0:1] range.
In addition, classes are provided in order to identify lower and upper limits for a dataset based on specific algorithms (such as using percentiles).

@@

\subsection{Utils}
% Lim

@@

The \package{astropy.stats} package provides
statistical tools that are useful for or specific to
astronomy and are not found in or extend the available
functionality of other \python\
statistics packages such as \package{scipy}
\citep{scipy} or \package{statsmodels}
\citep{seabold2010statsmodels}.   The
\package{stats} package contains a range of
different functionality used by many different
disciplines in astronomy.   It is not a complete set
of statistic tools, but rather a still growing
collection of useful features.

@@

%
\subsubsection{Robust Statistical Estimators}
\inlinecomment{BMS}{Can we highlight in a sentence for each of the ones below how they are different from e.g. the scipy equivalents?}
